Fluoroproj: Title to be decided later

### 2023-06-02 manuscript/manuscript.qmd
More friday progress

@@

Here are our results. Fear us.

Analysis ideas:

@@

Figure ideas:

-   scatterplots: ext chl/phyco on y, chl/phyco from each insturment on x, colors/shapes for each waterbody/culture

-   boxplots (need to be same units): first boxplot is extracted, compare to all others.

-   Scatterplot of historic waterbody chlorophyll vs chlorophyll from each instrument

>>>>

### Phytoplankton Counts

Add in stuff about sampling and Phycotech.

@@

### Summary of Data

Fig 1. Map of Field Sites

### Chlorophyll

Fig 2. Chlorophyll Scatterplot

### Phycocyanin

Fig 3. Phyco Scatterplot

### Phycocyanin to Chlorophyll Ratio

Fig 4. Ratio Scatterplot

### Phytoplankton Counts

@@
